\documentclass[]{article}
\usepackage{amssymb,amsmath}
\usepackage[english,finnish]{babel}
\usepackage{ifxetex,ifluatex}
\ifxetex
  \usepackage{fontspec,xltxtra,xunicode}
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\else
  \ifluatex
    \usepackage{fontspec}
    \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
    \newcommand{\euro}{€}
  \else
    \usepackage[utf8]{inputenc}
    \usepackage{eurosym}
  \fi
\fi
\usepackage{color}
\usepackage{fancyvrb}
\DefineShortVerb[commandchars=\\\{\}]{\|}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex,
              colorlinks=true,
              linkcolor=blue]{hyperref}
\else
  \usepackage[unicode=true,
              colorlinks=true,
              linkcolor=blue]{hyperref}
\fi
\hypersetup{breaklinks=true, pdfborder={0 0 0}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\title{Functional Programming Workshop}
\date{March 26, 2012}

\begin{document}
\maketitle
\thispagestyle{empty}

Pidämme kurssin funktionaalisesta ohjelmoinnista
\href{http://clojure.org}{Clojure}-ohjelmointikielellä.

\subsection{Kuvaus}

Clojure on nuorehko
\href{http://en.wikipedia.org/wiki/Lisp\_\%28programming\_language\%29}{Lisp}-sukuinen
ohjelmointikieli, joka tarjoaa funktionaalisen lähestymistavan
ohjelmointiin JVM-alustalla.

Kurssilla oletetaan ohjelmoinnin perustaidot Javalla, mutta ei
kuitenkaan funktionaalisen ohjelmoinnin taitoja.

Kurssi alkaa johdatuksella Clojuren käyttöön ja syntaksiin.
Alkulämmittelyn jälkeen keskitymme erityisesti ohjelmakokonaisuuksien
kirjoittamiseen.

Kurssi on viikon mittainen. Opetus keskittyy harjoitusten ja ohjelmien
tekemiseen.

Kurssin materiaali on englanniksi.

\otherlanguage{english}
\subsection{Description}

We're giving a course on functional programming with
\href{http://clojure.org}{Clojure}.

Clojure is a young
\href{http://en.wikipedia.org/wiki/Lisp\_\%28programming\_language\%29}{Lispish}
programming language. It is a functional programming language on the JVM
platform. Because it runs on the JVM, all Clojure programs can use the
standard and third-party Java libraries freely.

You should have basic Java programming skills. No prior experience with
functional programming is required.

The course starts with an introduction to Clojure; its syntax and
running it. After the introduction, we'll concentrate specifically on
writing whole programs.

The course is one week long with a focus on workshop sessions. The
course material is in English.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{(}\KeywordTok{defn}\FunctionTok{ hello }\NormalTok{[who]}
  \NormalTok{(}\KeywordTok{str} \StringTok{"Hello, "} \NormalTok{who }\StringTok{"!"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\end{document}
